Data Preparation, Integration and Cleaning

### 2017-03-09 abbDataAnalysis_Script.Rmd
clean up and integration of workflow

save(clean.count, daily.data, listing.data, ltr.data, pref.table,
     pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro, rawocc.type,
     pctocc.type, subm.data.ic, rawocc.geo, pctocc.geo, type.data.ic, pot.data.ic,
     s.subs, sssubs, str.data, str.data.ic, subs, all.mwl.coefs, all.mwl.surfs,
     core.suburbs, est.points, exch.rate, host.models, pref.models, prem.models,
     file=paste0(data.path, 'analyzed/analyzed_workspace.RData'))

>>>>

save(clean.count, daily.data, listing.data, ltr.data, pref.table,
     pref.table.wide, revdens.data, rawocc.metro, qtlocc.metro, rawocc.type,
     pctocc.type, subm.data.ic, rawocc.geo, pctocc.geo, type.data.ic, pot.data.ic,
     str.data, str.data.ic, subs,
     core.suburbs,  exch.rate, host.models, pref.models, prem.models,
     file=paste0(data.path, 'analyzed/analyzed_workspace.RData'))

 #all.mwl.coefs, all.mwl.surfs,est.points,  s.subs, sssubs,

### 2017-03-09 abbDataPrep_Script.Rmd
clean up and integration of workflow

  strtype.map <- ggplot() +
    geom_bar(data=str.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',gc()
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Short Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))

>>>>

  strtype.map <- ggplot() +
    geom_bar(data=str.data, aes(x=geo.mrkt, fill=geo.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) +
    #ggtitle('Short Term Property Type\nBy Submarket')+
    theme(plot.title = element_text(hjust = 0.5))
